Sea-ice and macrozooplankton distribution as determinants of top predator community structure in Antarctic winter

### 2024-06-07 analysis/paper/paper.qmd
Table 5

@@

make_fig_nmds(read_obj("nmds_envfit"),
              read_obj("nmds_df"),
              read_obj("nmds_sightings"),
              read_obj("nmds_env"))
```

>>>>

Note: an additional header row with "Mean", "Q1", and "Q3" columns must be created manually to produce the formatting seen in the published paper.

```{r}
#| label: tbl-clustenv
#| tbl-cap: "Summary of environmental conditions associated with predator clusters. See Table 1 for descriptions of environmental variables. Environmental variables that differed significantly (p < 0.05) between clusters are indicated with an asterisk (Kruskal-Wallis test with Bonferroni correction)."

make_clustenvtbl(read_obj("stations_clust"))

@@

# The NMDS figure is slightly stochastic, so setting the seed prevents minor 
# changes each time we render the paper
set.seed(1053)
make_fig_nmds(read_obj("nmds_envfit"),
              read_obj("nmds_df"),
              read_obj("nmds_sightings"),
              read_obj("nmds_env"))
```
